### 2023-02-16 notebooks/conformal.qmd
ufff
implemented loss functions definitely seem to make sense

```{julia}
M = CCE.ConformalModel(conf_model, mach.fitresult)
```

>>>>

## Counterfactual Explanation

```{julia}
M = CCE.ConformalModel(conf_model, mach.fitresult)
generator = CCE.ConformalGenerator()
```

```{julia}
x = select_factual(counterfactual_data,rand(1:size(counterfactual_data.X,2)))
y_factual = predict_label(M, counterfactual_data, x)[1]
target = counterfactual_data.y_levels[counterfactual_data.y_levels .!= y_factual][1]
```

```{julia}
p1 = contourf(mach.model, mach.fitresult, X, y; plot_classification_loss=true, target=target, zoom=0)
p2 = contourf(mach.model, mach.fitresult, X, y; plot_set_loss=true, zoom=0)
plot(p1, p2, size=(800,320))
```

```{julia}
ce = generate_counterfactual(x, target, counterfactual_data, M, generator)
```
